### 2024-06-30 docs/manuscript/manuscript.qmd
update on figures (r-values) and data (age)

81 community-dwelling older adults were recruited and selected by non-probabilistic sampling, from the Region of Magallanes and Chilean Antartica, Chile. They were included if: 65 years age or older; residents of the Region of Magallanes and Chilean Antarctica, Chile; and being able to understand the study aims and instructions. But they were excluded in case of: diagnosis of congenital heart disease; consumption of beta-blocker drugs, taking stimulant substances within 24 h before assessments session; motor or cognitive disability; inability to understand instructions or written content; or presence of pain during cardiac or physical assessments.

@@

```{r}
#| echo: false
#| warning: false
#| error: false
#| fig-width: 8
#| fig-height: 4
#| fig-dpi: 300
dat_long <- melt.data.table(
  data = dat,
  id.vars = c("id_record", "cc_grasa_total_porcentaje", "cc_masa_muscular_total"), 
  measure.vars = c("tm_pasos", "sppb_total")
)

@@

fig2a <- ggplot(dat_long, aes(value, cc_grasa_total_porcentaje)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("TMST steps", "SPPB total score")),
    cc_grasa_total_porcentaje = c(60, 60),
    value = c(42, 4),
    text = c("p = 0.013", "p = 0.015")
  ), size = 3.5, fontface = "italic") +
  labs(y = "Body fat (%)", x = NULL) +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist()

fig2b <- ggplot(dat_long, aes(value, cc_masa_muscular_total)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("TMST steps", "SPPB total score")),
    cc_masa_muscular_total = c(65.5, 65.5),
    value = c(42, 4),
    text = c("p = 0.541", "p = 0.584")
  ), size = 3.5, fontface = "italic") +
  labs(y = "Muscle mass (kg)", x = NULL) +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist()

@@

```{r}
#| echo: false
#| warning: false
#| error: false
#| fig-width: 8
#| fig-height: 8
#| fig-dpi: 300
dat_long <- melt.data.table(
  data = dat,
  id.vars = c("id_record", "tm_pasos", "sppb_total"), 
  measure.vars = c("hrv_sns_peri", "hrv_stress_peri", "hrv_rmssd_peri", "hrv_sdnn_peri", "hrv_pns_peri")
)

@@

fig3a <- ggplot(dat_long, aes(value, tm_pasos)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("RMSSD", "SDNN", "PNS index", "SNS index", "Stress index")),
    tm_pasos = c(125, 125, 125, 125, 125),
    value = c(13, 20, -2, 8, 45),
    text = c("p = 0.014", "p = 0.141", "p = 0.002", "p = 0.022", "p = 0.261")
  ), size = 3.5, fontface = "italic") +
  labs(y = "TMST steps", x = NULL) +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist() +
  theme(axis.line.x = element_blank(), axis.ticks.x = element_blank(), 
        axis.text.x = element_blank())

fig3b <- ggplot(dat_long, aes(value, sppb_total)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("RMSSD", "SDNN", "PNS index", "SNS index", "Stress index")),
    sppb_total = c(14, 14, 14, 14, 14),
    value = c(13, 20, -2, 8, 45),
    text = c("p = 0.010", "p = 0.419", "p < 0.001", "p = 0.006", "p = 0.095")
  ), size = 3.5, fontface = "italic") +
  labs(y = "SPPB score", x = "Values") +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist()

>>>>

81 community-dwelling older adults were recruited and selected by non-probabilistic sampling, from the Region of Magallanes and Chilean Antartica, Chile. They were included if: 55 years age or older; residents of the Region of Magallanes and Chilean Antarctica, Chile; and being able to understand the study aims and instructions. But they were excluded in case of: diagnosis of congenital heart disease; consumption of beta-blocker drugs, taking stimulant substances within 24 h before assessments session; motor or cognitive disability; inability to understand instructions or written content; or presence of pain during cardiac or physical assessments.

@@

```{r}
#| echo: false
#| warning: false
#| error: false
#| fig-width: 8
#| fig-height: 4
#| fig-dpi: 300
dat_long <- melt.data.table(
  data = dat,
  id.vars = c("id_record", "cc_grasa_total_porcentaje", "cc_masa_muscular_total", "sd_sexo"), 
  measure.vars = c("tm_pasos", "sppb_total")
)

@@

fig2a <- ggplot(dat_long, aes(value, cc_grasa_total_porcentaje)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point(aes(col = sd_sexo)) +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("TMST steps", "SPPB total score")),
    cc_grasa_total_porcentaje = c(60, 60),
    value = c(42, 4),
    text = c("p = 0.013\nr = -0.279", "p = 0.015\nr = -0.273")
  ), size = 3.5, fontface = "italic") +
  labs(y = "Body fat (%)", x = NULL) +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist()

fig2b <- ggplot(dat_long, aes(value, cc_masa_muscular_total)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("TMST steps", "SPPB total score")),
    cc_masa_muscular_total = c(65.5, 65.5),
    value = c(42, 4),
    text = c("p = 0.541\nr = -0.070", "p = 0.584\nr = -0.063")
  ), size = 3.5, fontface = "italic") +
  labs(y = "Muscle mass (kg)", x = NULL) +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist()

@@

```{r}
#| echo: false
#| warning: false
#| error: false
#| fig-width: 8
#| fig-height: 8
#| fig-dpi: 300
dat_long <- melt.data.table(
  data = dat,
  id.vars = c("id_record", "tm_pasos", "sppb_total", "sd_sexo"), 
  measure.vars = c("hrv_sns_peri", "hrv_stress_peri", "hrv_rmssd_peri", "hrv_sdnn_peri", "hrv_pns_peri")
)

@@

fig3a <- ggplot(dat_long, aes(value, tm_pasos)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point(aes(col = sd_sexo)) +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("RMSSD", "SDNN", "PNS index", "SNS index", "Stress index")),
    tm_pasos = c(125, 125, 125, 125, 125),
    value = c(13, 20, -2, 8, 45),
    text = c("p = 0.014\nr = -0.285", "p = 0.141\nr = -0.173", "p = 0.002\nr = -0.344", "p = 0.022\nr = 0.265", "p = 0.261\nr = 0.132")
  ), size = 3.5, fontface = "italic") +
  labs(y = "TMST steps", x = NULL) +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist() +
  theme(axis.line.x = element_blank(), axis.ticks.x = element_blank(), 
        axis.text.x = element_blank())

fig3b <- ggplot(dat_long, aes(value, sppb_total)) +
  facet_grid(~ variable, scales = "free_x") +
  geom_point(aes(col = sd_sexo)) +
  geom_smooth(method = "lm") +
  geom_text(mapping = aes(label = text), data = data.frame(
    variable = as.factor(c("RMSSD", "SDNN", "PNS index", "SNS index", "Stress index")),
    sppb_total = c(14, 14, 14, 14, 14),
    value = c(13, 20, -2, 8, 45),
    text = c("p = 0.010\nr = -0.294", "p = 0.419\nr = -0.095", "p < 0.001\nr = -0.375", "p = 0.006\nr = 0.313", "p = 0.095\nr = 0.194")
  ), size = 3.5, fontface = "italic") +
  labs(y = "SPPB score", x = "Values") +
  scale_y_continuous(expand = c(.1,.1)) +
  tidybayes::theme_ggdist()
